\textbf{Computational Fuzzy Extractors}

### 2013-06-14 trunk/CompFuzzExt.tex
added note about 5.3 working for arbitrary error distribution

>>>>

\thref{thm:blockLWE} holds for an arbitrary error distribution~(not just uniform error) in the following sense.  Let $\chi$ be an arbitrary error distribution.  Define $\chi'$ as the distribution where $m$ dimensions are sampled according to $\chi$ and the remaining dimensions have some fixed error.  Then, security of $\distLWE_{n, m, q, \chi}$ implies security of $\distLWE_{n+\alpha+ \beta, m+\alpha, q, \chi'}$.
